\textls[-0]{\thetitle}

### 2023-03-25 canonicitymodel.tex
parse
Typo.

    The color boxes indicate the scopes of the two instances of $\Gsub{\_}{\_}$.

@@

We note that, the interpretation of $\Wsup{i}{\wsig}{a}{b}$ is defined by $\CWsup$ (defined below) will take three elements, $i$, a glued $(\Gsub{\denotesCC{a}}{\Glued{\gm}})$ and a glued $(\Gsub{\denotesCC{b}}{{\Glued{\gm^\uparrow}}})$.  As we mentioned earlier, $\Glued{\gm}$ is the equivalent form of $(\gm, \gm')$.

@@

\begin{align*}
  \text{we define } \RecSig{}{} &\text{ by induction on the signature, via } RS \\
  RS~"nil"~R &= \denotesCC{\LSigEmp} \\
  RS~((A, B) :: tl)~R &= \GLSigAdd{RS~tl~R}{\Glued{\pi_2}}{\GCaseSig{A}{B}{R}} \\ 
  \denotesC{\goodType{\Gm}{\RecSig{\wsig}{"R"}}{}} &= \Gmodel{RS~\denotesC{\tau}~\denotesC{"R"}} \\
  \denotesC{\Recproj{j}{\lkg}} &= \text{ take the $j$-th field from } \lkg 
\end{align*}
\begin{align*}
  \denotesC{\goodTerm{\Gm}{\Wrec{\wsig}{\lkg}{t}}{T}}(\gm)(\gm') = \CWrec \quad &\Gsub{\denotesCC{\wsig}}{\Glued{\gm}} \\ 
  & (\lambda w. \denotesC{"R"}(\gm)(\gm')(\Wrec{\sub{\wsig}{\gm}}{\sub{\lkg}{\gm}}{w}))\\
  &f^r\\ &\sub{t}{\gm}\\ 
  &(\denotesC{t}(\gm)(\gm')) 
\end{align*}
\begin{align*}  
  \text{ where } \quad f^r~j~\Glued{a}~b~b^c &= 
  \texttt{let}~\Glued{\rho}  \in \GTm{
    \colorbox{blue!15}{(\Glued{\cdot} \Glued{,} \colorbox{blue!5}{\Gsub{\Glued{B}}{\GSubstExt{\Glued{"id"}}{\Glued{a}}}})}
    }{
      \colorbox{green!10}{(\Gsub{\Gsub{\Glued{R}}{\Glued{\gm}}}{\GSubstWeak{1}})}
    } 
  \\
  &\texttt{ s.t.}~\Glued{\rho} \coloneq (\Wrec{\wsig}{\sub{\lkg}{\SubstComp{\gm}{\SubstWeak{1}}}}{b},b^c)~\texttt{ in } \\
  & \Gmodel{
    \Gsub{
      \colorbox{blue!27}{\Gapp{
        \colorbox{blue!18}{\Gsub{
          \colorbox{blue!9}{\Gapp{
            \colorbox{blue!0}{\GRecproj{j}{\Gsub{\denotesCC{\lkg}}{\Glued{\gm}}}}
            }}
          }{
            \GSubstExt{\GSubstId}{\Glued{a}}
          }}}}
      }{
        \GSubstExt{\GSubstId}{\Glam{\Glued{\rho}}}
      }
    }(\epsilon)(\star) \\
  & \quad 
   \text{ given } \goodTerm{\Gm}{\lkg}{\RecSig{\wsig}{"R"}} \\
   & \quad \text{ where }\Glued{R} = \denotesCC{"R"}, \Glued{B} = \Gwsigproj{j}{2}{\denotesCC{\wsig}}
\end{align*}

>>>>

    The colored boxes indicate the scopes of the two instances of $\Gsub{\_}{\_}$.
    We use colored boxes here and below to help the reader parse nested glued interpretations.

@@

We note that, the interpretation of $\Wsup{i}{\wsig}{a}{b}$ is defined by $\CWsup$ (defined below). It will take three elements: $i$, a glued $(\Gsub{\denotesCC{a}}{\Glued{\gm}})$ and a glued $(\Gsub{\denotesCC{b}}{{\Glued{\gm^\uparrow}}})$.  As we mentioned earlier, $\Glued{\gm}$ is the equivalent form of $(\gm, \gm')$.

@@

\begin{align*}
  \text{we define } \RecSig{}{} &\text{ by induction on the signature, via } RS \\
  RS~"nil"~R &= \denotesCC{\LSigEmp} \\
  RS~((A, B) :: tl)~R &= \GLSigAdd{RS~tl~R}{\Glued{\pi_2}}{\GCaseSig{A}{B}{R}} \\ 
  \denotesC{\goodType{\Gm}{\RecSig{\wsig}{"R"}}{}} &= \Gmodel{RS~\denotesC{\tau}~\denotesC{"R"}} \\
  \denotesC{\Recproj{j}{\lkg}} &= \text{ take the $j$-th field from } \lkg 
\end{align*}
\begin{align*}
  \denotesC{\goodTerm{\Gm}{\Wrec{\wsig}{\lkg}{t}}{T}}(\gm)(\gm') = \CWrec \quad &\Gsub{\denotesCC{\wsig}}{\Glued{\gm}} \\ 
  & (\lambda w. \denotesC{"R"}(\gm)(\gm')(\Wrec{\sub{\wsig}{\gm}}{\sub{\lkg}{\gm}}{w}))\\
  &f^r\\ &\sub{t}{\gm}\\ 
  &(\denotesC{t}(\gm)(\gm')) 
\end{align*}
\begin{align*}  
  \text{ where } \quad f^r~j~\Glued{a}~b~b^c &= 
  \texttt{let}~\Glued{\rho}  \in \GTm{
    \colorbox{blue!15}{(\Glued{\cdot} \Glued{,} \colorbox{blue!5}{\Gsub{\Glued{B}}{\GSubstExt{\Glued{"id"}}{\Glued{a}}}})}
    }{
      \colorbox{green!10}{(\Gsub{\Gsub{\Glued{R}}{\Glued{\gm}}}{\GSubstWeak{1}})}
    } 
  \\
  &\texttt{ s.t.}~\Glued{\rho} \coloneq (\Wrec{\wsig}{\sub{\lkg}{\SubstComp{\gm}{\SubstWeak{1}}}}{b},b^c)~\texttt{ in } \\
  & \Gmodel{
    \Gsub{
      \colorbox{blue!27}{\Gapp{
        \colorbox{blue!18}{\Gsub{
          \colorbox{blue!9}{\Gapp{
            \colorbox{blue!0}{\GRecproj{j}{\Gsub{\denotesCC{\lkg}}{\Glued{\gm}}}}
            }}
          }{
            \GSubstExt{\GSubstId}{\Glued{a}}
          }}}}
      }{
        \GSubstExt{\GSubstId}{
          \colorbox{green!10}{\Glam{\Glued{\rho}}}
          }
      }
    }(\epsilon)(\star) \\
  & \quad 
   \text{ given } \goodTerm{\Gm}{\lkg}{\RecSig{\wsig}{"R"}} \\
   & \quad \text{ where }\Glued{R} = \denotesCC{"R"}, \Glued{B} = \Gwsigproj{j}{2}{\denotesCC{\wsig}}
\end{align*}
